From physical principles to classical Hamiltonian mechanics

### 2014-07-17 2014ClassicalHamiltonianDerivation/classicalHamiltonianDerivation.tex
Fixed warnings
Switching to revtex 4.1 fixes the footnotes on last page!
Removing unneeded theorem definitions
Changing affiliation and e-mail address
Update title and contact info

%\documentclass[aps,prd,twocolumn,floatfix]{revtex4}   % style for Physical Review B and AJP are similar
\documentclass[twocolumn,floatfix,nofootinbib]{revtex4}   % style for Physical Review B and AJP are similar
%\documentclass[12pt,aps,prb,preprint]{revtex4}

@@

\theoremstyle{theorem}
\newtheorem{thm}{Theorem}[section]
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{sublem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{ax}[thm]{Axiom}
\newtheorem{conj}[thm]{Conjecture}
\newtheorem{clm}[thm]{Claim}
\newtheorem{lemdef}[thm]{Lemma-Definition}

\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\newtheorem{rem}[thm]{Remark}
\newtheorem{ques}[thm]{Question}
\newtheorem{cons}[thm]{\rm\bfseries{Construction}}
\newtheorem{exm}[thm]{Example}
\newtheorem{conds}[thm]{Condition}
\newtheorem{proper}[thm]{Property}
\newtheorem{defnlem}[thm]{Definition-Lemma}
\newtheorem*{assump1}{Classical assumption}
\newtheorem*{assump2}{Determinism and Reversibility assumption}
\newtheorem{warn}[thm]{Warning}
\newtheorem{situ}[thm]{Situation}

@@

\title{From physical principles to Hamiltonian mechanics}
\author{Gabriele Carcassi}
\affiliation{Brookhaven National Laboratory, Upton, NY 11973}
\email{carcassi@bnl.gov}
\date{May 23, 2014}

@@

\begin{thebibliography}{5}

>>>>

\documentclass[aps,pra,10pt,twocolumn,floatfix,nofootinbib]{revtex4-1}

@@

\newtheorem{thm}{Theorem}[section]
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}

\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\newtheorem*{assump1}{Classical assumption}
\newtheorem*{assump2}{Determinism and Reversibility assumption}

@@

\title{From physical principles to classical Hamiltonian mechanics}
\author{Gabriele Carcassi}
\affiliation{University of Michigan, Ann Arbor, MI 48109}
\email{carcassi@umich.edu}
\date{June 16, 2014}

@@

\begin{thebibliography}{0}
